That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-23 ms.tex
blah

We also obtained a good fit with the moon model; however, the addition of three more free parameters does not significantly improve the fit quality. The best fit moon model has a radius $r_\mathrm{moon} = 2.4R_\oplus$, a mid-transit time $t_\mathrm{moon} = 2458055.2869\,\mathrm{BJD_{TDB}}$, and a period $P_m = 26.5$ days. This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but the $\chi_\nu^2$ is unchanged (also $1.05$). According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, the moon transit time is not well-constrained by the data. As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire visit.  The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.

@@

Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction. The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data). As TK18 found, the moon model improves the rms to 363.4 ppm ($\Delta\chi^2 = 22.0$); however, even with the additional four free parameters, the moon model does not perform as well as the no-moon model fit to our data.  This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.  
%Even when a moon is included, the fit is still slightly worse (rms of 363.4 ppm) than our best no-moon model, in spite of four additional free parameters.

>>>>

We also obtained a good fit with the moon model; however, the addition of three more free parameters does not significantly improve the fit quality. The best fit moon model has a radius $r_\mathrm{moon} = 2.4R_\oplus$, a mid-transit time $t_\mathrm{moon} = 2458055.2869\,\mathrm{BJD_{TDB}}$, and a period $P_m = 26.5$ days. This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but the $\chi_\nu^2$ is unchanged (also $1.05$). According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, the moon transit time is not well-constrained by the data. As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire duration of the observations.  The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.

@@

%Similar to the finding of TK18, the moon model improves the fit quality by a $\Delta\chi^2 = 22.0$. However, even with the moon included, the model does not perform better than our no-moon fit (rms = 363 versus 362 ppm). This differenc

%Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction. The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data).

Similar to the finding of TK18, the moon model improves the fit quality by a $\Delta\chi^2 = 22.0$; however, even with the additional four free parameters, the moon model does not perform better than the no-moon model fit to our data (rms of 363 versus 362 ppm).  This difference in fit quality --- equivalent rms to within 1 ppm, but four additional parameters --- corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.  
%Even when a moon is included, the fit is still slightly worse (rms of 363.4 ppm) than our best no-moon model, in spite of four additional free parameters.
